%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{tabularx}{\textwidth}{X>{\centering\arraybackslash}X>{\raggedleft\arraybackslash}X}
Indianapolis, IN & \textbf{\LARGE Justin Hartman} & justinhartman@outlook.com \\
(765) 720-4268 & \href{https://justinhartman.me}{justinhartman.me} & \href{https://justinhartman.me}{justinhartman.me} \\
\end{tabularx}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Purdue University}{West Lafayette, IN}
      {Bachelor of Science in Computer Science}{Aug. 2016 -- May 2020}
        \resumeItemListStart
            \resumeItem{Degree focus in computer graphics and visualization}
            \resumeItem{Certificate in Entrepreneurship and Innovation}
        \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior iOS Engineer}{Oct. 2022 -- Present}
      {Fleetio}{Birmingham, AL}
      \resumeItemListStart
        \resumeItem{Implement features in \textbf{Swift} for Fleetio Go, a mobile app with 125,000+ monthly users.}
        \resumeItem{Lead team initiative to develop a Design Language system, building low-level \textbf{SwiftUI} components to standardize the app's design and introduce dark mode functionality.}
        \resumeItem{Migrate existing \textbf{UIKit} view to \textbf{SwiftUI}, improving the app's performance and user experience.}
        \resumeItem{Build prototypes with various native integrations such as \textbf{App Clips, ARKit, and CoreML.}}
        \resumeItem{Utilize \textbf{Bitrise, Runway, Fastlane, and Firebase} to implement CI/CD for internal QA testing and deployments.}
      \resumeItemListEnd

    \resumeSubheading
      {iOS Software Engineer}{March 2020 -- Oct. 2022}
      {Bloomerang}{Indianapolis, IN}
      \resumeItemListStart
        \resumeItem{Implement features in \textbf{Swift, Kotlin, and C\#} for iOS and Android applications.}
        \resumeItem{Create custom \textbf{C\#} binding libraries for a payment processing SDK that connects Bluetooth credit card readers to a cross-platform \textbf{Xamarin} app.}
        \resumeItem{Utilize \textbf{Jenkins, Fastlane, and Azure Pipelines} to implement CI/CD for internal QA testing.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer Intern}{May. 2019 -- Aug. 2019}
      {PFL}{Indianapolis, IN}
      \resumeItemListStart
        \resumeItem{Designed and made an internal tool using \textbf{C\#} for automating the process of resubmitting failed messages within \textbf{Azure Service Bus.}}
        \resumeItem{Tool was designed with flexibility to handle any message error defined within its configuration.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineer Intern}{May 2018 -- Aug. 2018}
      {State Farm}{Bloomington, IL}
      \resumeItemListStart
        \resumeItem{Worked on a big data web application, doing full stack development on an agile team.}
        \resumeItem{Tasks ranged from creating \textbf{Python} automation scripts, adding frontend features with \textbf{React}, and data manipulation with \textbf{Scala}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{bunbox} $|$ \emph{Swift, Typescript, PostgresSQL, Git}}{Aug. 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Developing an iOS app to import, organize, and share recipes.}
            \resumeItem{Using \textbf{CoreML} to analyze input images/text to determine ingredients, instructions, and cooking times.}
            \resumeItem{Adding a web-based interface, built with vanilla \textbf{Typescript}, for non-users to view recipe links.}
            \resumeItem{Using \textbf{Supabase} for auth and database management.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Bearly Delivered} $|$ \emph{Godot Engine, GDScript, C++, Blender}}{Dec. 2021 -- May 2025}
          \resumeItemListStart
            \resumeItem{Developed an arcade style physics game where you attempt to deliver packages around your procedurally generated neighborhood.}
            \resumeItem{Implemented custom physics properties, terrain/road generation, and NPC behaviors.}
            \resumeItem{Published to Steam and designed the game's logo and marketing materials.}
            \resumeItem{Prototyped CI/CD pipelines using GitHub Actions to automate deployment.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Swift, Kotlin, C\#, JavaScript, HTML, CSS, Python, C/C++, Java} \\
     \textbf{Frameworks}{: VisonKit, CoreML, Xamarin, React/React Native, AWS, GraphQL} \\
     \textbf{Developer Tools}{: Git, Xcode, Bitrise, Runway, Firebase, Github Actions, Supabase} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}